Coexistence with varying environmental filtering intensity

### 2018-07-02 env_intensity.Rmd
:sparkles: Growth landscape + scale trait value
Co-authored-by: Rekyt <matthias.grenie@ens-lyon.fr>
Co-authored-by: pierredenelle <pierre.denelle@cefe.cnrs.fr>

    res = lapply(seq(n_other), function(x) {
        x2 = runif(number_patches, 1, number_patches)

        cov_mat %*% matrix(c(x1, x2), nrow = 2, byrow = TRUE)
    })

@@

    t(res)
}

@@

# Number of trait influencing growth or competition
trait_types = t(data.frame(prop_8_2 = c(rep("R", round(0.8*n_traits)),
                                        rep("A", n_traits - round(0.8*n_traits))),
                           prop_5_5 = c(rep("R", round(0.5*n_traits)),
                                        rep("A", n_traits - round(0.5*n_traits))),
                           prop_2_8 = c(rep("R", round(0.2*n_traits)),
                                        rep("A", n_traits - round(0.2*n_traits)))))
colnames(trait_types) = colnames(traits)

# Simulations ------------------------------------------------------------------
multiple_traits <- apply(trait_types, 1,
                         function(x){
                             multiple_traits_types = multigen(traits = traits, trait_type = x,
                                                              env = env, time = time, species = species,
                                                              patches = patches, composition = composition,
                                                              A = A, d = d, k = k, width = width)
                         })
names(multiple_traits) <- rownames(trait_types)

@@

# Plot individual patches 
plot_patches_list <- lapply(names(multiple_traits),
                            function(x){
                                plot_patch(multiple_traits[[x]]$compo, 15, 150) +
                                    labs(subtitle = x)
                            })

@@

>>>>

    res = lapply(seq(n_other), function(x) {

        # Independent trait
        x2 = runif(number_patches, 1, number_patches)

        # Correlated trait in second row
        cov_mat %*% matrix(c(x1, x2), nrow = 2, byrow = TRUE)

    })

@@

    res = t(res)

    # Repaste first column
    cbind(res[,1],

          # Scale all the traits between min and max value of x1
          sapply(2:ncol(res), function(x) {
              val = res[,x]

              (val - min(val))/(max(val) - min(val)) * (diff(range(x1))) +
                  min(x1)
          }))
}

@@

# Number of trait influencing growth or competition
trait_types = t(data.frame(R8_A2 = c(rep("R", round(0.8*n_traits)),
                                     rep("A", n_traits - round(0.8*n_traits))),
                           R5_A5 = c(rep("R", round(0.5*n_traits)),
                                     rep("A", n_traits - round(0.5*n_traits))),
                           R2_A8 = c(rep("R", round(0.2*n_traits)),
                                     rep("A", n_traits - round(0.2*n_traits)))))
colnames(trait_types) = colnames(traits)

# Simulations ------------------------------------------------------------------
multiple_traits <- apply(trait_types, 1,
                         function(x){
                             multigen(traits = traits,
                                      trait_type = x,
                                      env = env,
                                      time = time,
                                      species = species,
                                      patches = patches,
                                      composition = composition,
                                      A = A, d = d,
                                      k = k, width = width)
                         })
names(multiple_traits) <- rownames(trait_types)

@@

# Plot individual patches 
plot_patches_list <- lapply(names(multiple_traits),
                            function(x){
                                single_patch =
                                    plot_patch(multiple_traits[[x]]$compo, 15,
                                               150) +
                                    labs(subtitle = x)

                                directlabels::direct.label(single_patch)
                            })

@@

Additional plot to show number of individuals in function of distance to trait that suffer from maximum competition and distance to optimal patch value.

```{r}
library("tidyverse")

landscape_df = function(multiple_traits_scenario, trait_types_row) {

    growth_traits = names(trait_types_row[trait_types_row %in% c("R", "RA")])
    compet_traits = names(trait_types_row[trait_types_row %in% c("A", "RA")])

    population_df = multiple_traits_scenario$compo[,,150] %>%
        as.data.frame() %>%
        rownames_to_column("patch") %>%  # Add patch names as column
        # Transform to tidy data.frame (define name of columns and column name for values)
        gather("species", "N", -patch)

    growth_df = enframe(rowMeans(traits[, growth_traits, drop = FALSE]),
                        "species", "optim_env")

    compet_df = enframe(abs(rowMeans(traits[, compet_traits, drop = FALSE]) -
                                12.5), "species", "compet_dist")

    population_df %>%
        inner_join(growth_df, by = "species") %>%
        inner_join(compet_df, by = "species") %>%
    # Add patch number as a new column and compute distance to optimal value
    mutate(patch_optim = gsub("patches", "", patch) %>%
               as.numeric(),
           optim_dist = abs(optim_env - patch_optim))
}

all_landscape = lapply(names(multiple_traits), function(scenario) {
    landscape_df(multiple_traits[[scenario]], trait_types[scenario,])
})
names(all_landscape) = names(multiple_traits)

all_land = bind_rows(all_landscape, .id = "simulation_type")

lalaland = ggplot(all_land, aes(compet_dist, optim_dist)) +
    stat_summary_2d(aes(z = N)) +
    facet_wrap(~simulation_type) +
    scale_fill_viridis_c(trans = "log10") +
    scale_x_reverse() +
    labs(x        = "Distance to Maximum Competition\n(0 = species experiences maximum competition)",
         y        = "Distance to Optimal Environmental Value",
         fill     = "Number of Individuals at t=150",
         subtitle = "Growth and Competition Landscape") +
    theme_bw() +
    theme(legend.position = "bottom")

plot_laughlin = ggplot(all_land, aes(optim_env, patch_optim)) +
    stat_summary_2d(aes(z = N)) +
    facet_wrap(~simulation_type, labeller = c(R2_A8 = "20% Growth\n80% Competiton",
                                              R5_A5 = "50% Growth\n50% Competiton",
                                              R8_A2 = "80% Growth\n20% Competiton") %>%
                   as_labeller()) +
    scale_fill_viridis_c(trans = "log10") +
    labs(x    = "Species Optimum",
         y    = "Environmental Value",
         fill = "Number of Individuals") +
    theme_bw() +
    theme(legend.position = "bottom")
```
